How Old Actors?

### 2017-08-15 01_actor_careers/05_report.Rmd
Working on JS interactivity

---
title: "How Old Actors?"
output: html_document
---

@@

```{r}
library(readr)
library(dplyr)

films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/full_film_data.csv") %>%
  filter(!is.na(title))

films %>% glimpse()

@@

film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/actors_directors.csv")

@@

@@

>>>>

---
title: "How Old Actors?"
output: 
  html_document:
    code_folding: hide
---

@@

```{r}
library(readr)
library(dplyr)
library(tidyr)

films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>%
  filter(!is.na(title))

@@

film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")

@@

## Gender Gap

Some text.
Some text.
Some text.
Some text.Some text.
Some text.
Some text.
Some text.
Some text.
Some text.
Some text.

```{r}
library(highcharter)
tmbish = 
  hc_theme(
    chart = list(
      backgroundColor = list("white"),
      style = list(
        fontFamily = "Droid Sans"
      )
    ),
    colors = list("#414141", "#FF6A5C", "#CCDFC8", "#056571"),
    title = list(
      style = list(fontWeight = "bold", color = "#414141"),
      align = "left"
    ),
    xAxis = list(
      gridLineColor = "#2196F3",
      lineColor = "#2196F3",
      gridLineWidth = 0.5,
      lineWidth = 0,
      title = list(style = list(fontWeight = "bold"))
    ),
    yAxis = list(
      gridLineColor = "#2196F3",
      lineColor = "#2196F3",
      gridLineWidth = 0.5,
      lineWidth = 0,
      title = list(style = list(weight = "bold"))
    ),
    subtitle = list(
      style = list(fontStyle = "italic", color ="#414141"), 
      align = "left"
    ),
    tooltip = list(
      borderWidth = 0,
      shape = "square",
      valueDecimals = 2
    )
  )

volume_data =
  films %>% 
  select(title, year, tomatometer, director, actor_1:actor_3) %>%
  gather("role", "name", director, actor_1:actor_3) %>%
  mutate(role = ifelse(role == "director", "Director", "Actor")) %>%
  inner_join(film_folk) %>%
  mutate(
    age_at_production = year - dob_year
  ) %>%
  filter(between(age_at_production, 10,100)) %>%
  select(name, gender, dob_year, age_at_production, year, role, tomatometer)

  temp = 
    volume_data %>%
    filter(
      !is.na(gender)
    ) %>%
    mutate(
      category = case_when(
        role == "Director" ~ "director",
        gender == "male" ~ "male_actor",
        TRUE ~ "female_actor"
      )
    ) %>% 
    group_by(category, age_at_production) %>%
    summarise(films = n()) %>%
    group_by(category) %>%
    mutate(percentage = films / sum(films))

<div id = "tester">
```{r}
chart_data = 
temp %>%
select(-films) %>%
spread(category, percentage) %>%
mutate(
  director_cdf = cumsum(ifelse(!is.na(director), director, 0)),
  female_actor_cdf = cumsum(ifelse(!is.na(female_actor), female_actor, 0)),
  male_actor_cdf = cumsum(ifelse(!is.na(male_actor), male_actor, 0))
)

female_cdf = chart_data$female_actor_cdf
female_pdf = chart_data$female_actor
male_cdf = chart_data$male_actor_cdf
male_pdf = chart_data$male_actor
dir_cdf = chart_data$director_cdf %>% round(2)
dir_pdf = chart_data$director

chart = 
  highchart() %>%
  hc_add_theme(tmbish) %>%
  hc_xAxis(
    categories = chart_data$age_at_production,
    title = list(text = "Age at Production")
  ) %>%
  hc_yAxis(
    labels = list(formatter = JS("function(){return(Math.round(this.value * 1000) / 10 + '%')}"))
  ) %>%
  hc_title(text = "Female actors") %>%
  hc_subtitle(text = "Comparing male actors, (male) directors and female actors") %>%
  hc_add_series(name = "Director", type = "spline", data = chart_data$director) %>%
  hc_add_series(name = "Male Actor", type = "spline", data = chart_data$male_actor) %>%
  hc_add_series(
    name = "Female Actor",
    type = "area",
    data = chart_data$female_actor,
    zIndex = -10,
    marker = list(enabled = FALSE),
    fillOpacity = 0.5
  )

chart
```
</div>

<button id = "button">Button</button>

@@

## Housekeeping

<script>

$(document).ready(function() {
    $("#button").click(function(){

        var chart=$("#tester").find(".highchart").highcharts();

        if (chart.yAxis[0].getExtremes().dataMax == 1) {

        } else {

          chart.yAxis[0].setExtremes(0,`1`);
          data = `dir_cdf`;
          alert(data);
          <!--chart.series[0].setData(`JS(paste0("[", dir_cdf %>% paste(collapse = ","), "]"))`); -->
        };

    }); 
});

</script>
